Download data

### 2023-12-29 scripts/download_independent_variables.Rmd
replacing N NAs with 0 in three rasters

>>>>

these layers have NAs which we will treat as 0s
```{r eval = F}

p <- '/media/steppe/hdd/Geospatial_data/WesternPlantPredictors2/chelsa'
paths <- list.dirs(p, recursive = T)

maskR <- vrt(file.path(p, 'bio1', list.files(file.path(p, 'bio1'))))

gdgfgd10 <- vrt(file.path(p, 'gdgfgd10_old', list.files(file.path(p, 'gdgfgd10_old'))))
gdgfgd5 <- vrt(file.path(p, 'gdgfgd5_old', list.files(file.path(p, 'gdgfgd5_old'))))
swe <- vrt(file.path(p, 'swe_old', list.files(file.path(p, 'swe_old'))))

gdgfgd10 <- subst(gdgfgd10, NA, 0)
gdgfgd10 <- mask(gdgfgd10, maskR) # remove the ocean/set extent again
filename <- paste0(p, '/gdgfgd10/', 'gdgfgd10_.tif')
makeTiles(gdgfgd10, template, filename)

gdgfgd5 <- subst(gdgfgd5, NA, 0)
gdgfgd5 <- mask(gdgfgd5, maskR) # remove the ocean/set extent again
filename <- paste0(p, '/gdgfgd5/', 'gdgfgd5_.tif')
makeTiles(gdgfgd5, template, filename)

swe <- subst(swe, NA, 0)
swe <- mask(swe, maskR) # remove the ocean/set extent again
filename <- paste0(p, '/swe/', 'swe_.tif')
makeTiles(swe, template, filename)

rm(gdgfgd10, gdgfgd5, swe, p, paths, maskR)
```
